Safe Transferable Regions

### 2016-10-06 paper/type-inference.tex
constraint solver

\begin{lemma}
  Consider any constraint satisfying the above invariant with a rhs of the
  form $\pi_i \outlives \pi_j$, with both $\pi_i$ and $\pi_j$ region constants.
  (a) If $\{ \pi_i, \pi_j \} \subseteq \predDeltaMap(\varphi)$,
  then $\isvalid{\varphi}{\pi_i \outlives \pi_j}$ in any solution to the constraints.
  (b) If $\{ \pi_i, \pi_j \} \not \subseteq \predDeltaMap(\varphi)$,
  then $\isvalid{\phicx}{\pi_i \outlives \pi_j}$ in any solution to the constraints.
\end{lemma}

>>>>

\begin{lemma}
  Consider any decomposable constraint  $\isvalid{\varphi \conj \phi}{\pi_i \outlives \pi_j}$
where both $\pi_i$ and $\pi_j$ are region constants.
(a) If $\{ \pi_i, \pi_j \} \subseteq \predDeltaMap(\varphi)$,
then $\soln$ satisfies $C \cup \{ \isvalid{\varphi \conj \phi}{\pi_i \outlives \pi_j} \}$
iff
$\soln$ satisfies $C \cup \{ \isvalid{\varphi}{\pi_i \outlives \pi_j} \}$
  (b) If $\{ \pi_i, \pi_j \} \not \subseteq \predDeltaMap(\varphi)$,
$\soln$ satisfies $C \cup \{ \isvalid{\varphi \conj \phi}{\pi_i \outlives \pi_j} \}$
iff
$\soln$ satisfies $C \cup \{ \isvalid{\phi}{\pi_i \outlives \pi_j} \}$
\end{lemma}

Note that the above lemma shows how the conjunction in the antecedent of
any decomposable constraint can be eliminated.
